Title page

### 2024-09-04 output/Title_page.Rmd
Creates title page docx template

---
output:
  officedown::rdocx_document:
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
editor_options: 
  chunk_output_type: console
---

>>>>

---
output:
  officedown::rdocx_document:
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Title_page_template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
editor_options: 
  chunk_output_type: console
---
